---
title: "Alcohol vs Seat choice"
author: "Netalia Ventura"
date: "March 3, 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The median drinks are higher in the back row compared to the median drinks in the front and middle rows. We're able to determine that from the boxes above on the graph. 
  

### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
There are these; we're going to call them "bites" on the boxes that are on the plot above. These represent the standard deviation, which is the amount of drinks consumed.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
  
The chart above shows that the back row is at 12.580471, while front is at 3.806013 and the middle at 6.225381. Proving that our guess that the back row had a higher consumtion of alcohol.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
We reject the null hypothesis because the results indicate that the chances are 1 out of 10,000. making the number significantly low showing at 0.000116.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
  
Now that we have the box properly labeled, we can see on the graph that the zero is the only one in the confidence inner poll and is in the middle of the front and middle rows. Which is telling us that the back is different than both of the other rows. Making it that there is no statistical difference between both the front and the middle.

## Conclusions


  

